\hiddenchapter{{\large{B}ACKGROUND}}
\ChapterTitle[\thechapter]{BACKGROUND}

\hiddensection{{\large{D}}OMAIN}
\SectionTitle{\thesection}{DOMAIN}
\\

Students and researchers in nowadays frequently rely on digital tools to explore scientific topics, search for academic documents, and understand complex terminology. Although AI chatbots and academic search engines exist, they often lack the connectivity of terminologies and information structure that helps users truly understand the context and relationships between scientific terms. Traditional research workflows such as searching, reading papers, taking notes and organizing concepts remain inefficient and time consuming, where time is mainly focused on the research flow itself not the actual knowledge.
\\
\hiddensection{{\large{E}}XITSTING APPROACHES AND LIMITATIONS}
\SectionTitle{\thesection}{EXISTING APPROACHES AND LIMITATIONS}
\\

The Internet is flooded with AI-assisted academic tools, such as semantic search engines, PDF analyzers, and AI chatbots. However, Search engines return documents but do not explain how ideas relate. AI chatbots provide answers but do not maintain backlinks or concept relationships. Knowledge graphs exist in theoretical research, but applications generate them dynamically based on user queries. Note-taking tools are separate from search and explanation workflows, causing  fragmentation. 
No existing system merges \textbf{semantic search, conversational AI, knowledge graph, and notebook} into a unified and personalized research environment. 
\\\\
Here, a graph showing possible competitors is presented.

\begin{table}[h!]
\centering
\small
\caption{Compact Comparison Between Scholar Mind and Competitors}
\begin{tabular}{lcccc}
\hline
\textbf{Tool} & 
\textbf{Semantic Search} & 
\textbf{AI Chat} & 
\textbf{Knowledge Graph} & 
\textbf{PDF Upload} \\
\hline
Google Scholar & Yes & No & No & No \\
Semantic Scholar & Yes & No & No & No \\
Connected Papers & No & No & Yes & No \\
ResearchRabbit & No & No & Yes & No \\
Elicit AI & Yes & Yes & No & Yes \\
Perplexity AI & Yes & Yes & No & No \\
ChatGPT & Partial & Yes & No & Yes \\
Zotero & No & No & No & Yes \\
NotebookLM & No & Yes & No & Yes \\
Bohrium & No & Yes & No & Yes \\
\textbf{ScholarMind}& Yes & Yes & Yes & Yes \\
\hline
\end{tabular}
\end{table}


\clearpage